\documentclass[pdflatex,sn-mathphys]{sn-jnl} % Springer Nature template for NCA

%------------------------------------------------------------------------------
% PACKAGES
%------------------------------------------------------------------------------
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{float}
\usepackage{subcaption}
\usepackage{caption}
\usepackage[table]{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true, allcolors=blue}
\usepackage{textcomp}
\usepackage[numbers]{natbib}
\usepackage{rotating}
\raggedbottom

%------------------------------------------------------------------------------
% BEGIN DOCUMENT
%------------------------------------------------------------------------------
\begin{document}

%------------------------------------------------------------------------------
% TITLE AND AUTHORS
%------------------------------------------------------------------------------
\title[Satellite Crop Classification]{Temporal Patterns and Pixel Precision: Satellite-Based Crop Classification Using Deep Learning and Machine Learning}
\makeatletter
\renewcommand{\@makefnmark}{\textsuperscript{*}}
\renewcommand{\footnoterule}{
  \kern -3pt
  \hrule width 2cm height 0.4pt
  \kern 2.6pt
}
\makeatother
\footnotetext{Corresponding author: Disha Kacha, disha.kacha@gwu.edu}
\author[1]{\fnm{Sairam} \sur{Venkatachalam}}\email{sairam.venkatachalam@gwu.edu}
\author[1]{\fnm{Disha} \sur{Kacha}}\email{disha.kacha@gwu.edu}
\author[1]{\fnm{Devarsh} \sur{Sheth}}\email{devarshapurva.sheth@gwu.edu}
\author[2]{\fnm{Michael} \sur{Mann}}\email{mmann1123@email.gwu.edu}
\author[2]{\fnm{Amir} \sur{Jafari}}\email{ajafari@email.gwu.edu}

\affil{\orgdiv{Department of Geography \& Environment and the Data Science Program}, \orgname{The George Washington University}, \city{Washington}, \state{DC}, \country{USA}}
\maketitle
%------------------------------------------------------------------------------
% DECLARATIONS
%------------------------------------------------------------------------------
\section*{Declarations}
\textbf{Ethics Approval:} This study did not involve human participants or animal subjects and therefore did not require ethics approval.

\noindent\textbf{Consent to Participate:} This study did not involve human participants, so consent to participate was not required.

\noindent\textbf{Consent for Publication:} This study does not include identifiable personal data, so consent for publication is not applicable.


\noindent\textbf{Availability of data and material:} The datasets generated and/or analyzed during the current study are available from the corresponding author on reasonable request.

\noindent\textbf{Competing interests:} The authors declare that they have no competing interests.

\noindent\textbf{Funding:} This research received no external funding.

\noindent\textbf{Author Contributions:} Sairam Venkatachalam, Disha Kacha, and Devarsh Sheth collectively contributed to the project design, data processing, model development, experimentation, and analysis. All authors were involved in manuscript writing, review, and final approval.

\noindent\textbf{Acknowledgements:} The authors would like to thank Professor Michael Mann and Dr. Amir Jafari from The George Washington University for their valuable guidance, mentorship, and support throughout the research.

\end{document}